R Coding Exercise

### 2024-08-02 Group 10 Final Project/manuscript_final-2.qmd
More work on profile
update

---
title: "Honey Bee Colonies Impacted by Varroa, American Foulbrood and Global Warming"
subtitle: ""
author: Edward Cruz, Jr., Leonel G. Salazar, Amelia Tristan, Mojisola Popoola
date: today
format:
  html:
    toc: false
    number-sections: true
    highlight-style: github
editor: 
  markdown: 
    wrap: 72
---

@@

>>>>

---
title: "R Coding Exercise"
---

@@

```{r}
# Install necessary packages
install.packages("DiagrammeR")

# Load the DiagrammeR package
library(DiagrammeR)

# Create the flowchart using DiagrammeR
grViz("
  digraph Data_Analysis_Flowchart {
    graph [layout = dot, rankdir = TB]

    node [shape = box, style = filled, color = lightblue]

    Define_Objectives [label = 'Define Objectives']
    Collect_Data [label = 'Collect Data']
    Clean_Data [label = 'Clean Data']
    Analyze_Data [label = 'Analyze Data']
    Interpret_Results [label = 'Interpret Results']
    Visualize_Data [label = 'Visualize Data']
    Compile_Report [label = 'Compile Report']
    Review_Revise [label = 'Review & Revise']
    Present_Report [label = 'Present Report']

    Define_Objectives -> Collect_Data
    Collect_Data -> Clean_Data
    Clean_Data -> Analyze_Data
    Analyze_Data -> Interpret_Results
    Interpret_Results -> Visualize_Data
    Visualize_Data -> Compile_Report
    Compile_Report -> Review_Revise
    Review_Revise -> Present_Report
  }
")
```
